refnx -- Neutron and X-ray reflectometry analysis in Python

### 2018-07-24 paper/manuscript.tex
Include conda ref at distribution text

 The recommended way of using \refnx\ is from a \conda\ environment (a package, dependency and environment manager for software), using the pre-compiled distributables on the \refnx\ conda-forge channel. These distributables are made as part of the release process using the same CI web-services used to test the code. The matrix of distributables cover the major Python versions currently in use, across the macOS/Windows/Linux operating systems. Alternatively the package can be installed from source, either directly from the git repository, or via \pip\ from the version uploaded to PyPI (https://pypi.python.org/pypi/refnx). Building from source requires a C compiler and the \Cython\ and \NumPy\ packages to be installed.

>>>>

The recommended way of using \refnx\ is from a \conda\ environment, which offers package, dependency and environment management \cite{conda}, using the pre-compiled distributables on the \refnx\ conda-forge channel. These distributables are made as part of the release process using the same CI web-services used to test the code. The matrix of distributables cover the major Python versions currently in use, across the macOS, Windows, and Linux operating systems. Alternatively the package can be installed from source, either directly from the git repository, or via \pip\ from the version uploaded to PyPI. \footnote{https://pypi.python.org/pypi/refnx} Building from source requires a C compiler and the \Cython\ and \NumPy\ packages to be installed.
